A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-28 5_generalization.tex
better describe boundary conditions in beading scheme

The following restrictions hold:
\begin{enumerate}
\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item $B$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
%\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
%\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is positive, monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
\end{enumerate}

>>>>

The following restrictions hold:
\begin{enumerate}
\item Transitions shouldn't overlap each other: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item Beadings are symmetric from the center: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
%\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
%\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is positive, monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
\end{enumerate}
